Time Series Bootstrapping For Solar Current

### 2021-12-16 deliverables/paper.Rmd
discussions
I ended up using just the HOUR_WINDOW as our range of peak hours.

The power estimate generated in this study has practical applications in real-world electrical engineering problems. An allocation must be made that balances the expected contribution of renewable energy sources with the expected residual demand on the electrical grid. An intelligent estimate of the contribution from PV modules must account for geographical deviations in solar irradiance. While the estimate here was made for Los Angeles, this framework can be applied to any location for which irradiance data is tracked. This framework could also be applied to intervals of time where power estimates could be made for each hour of the day or for each day of the year; greater stratified specificity would improve the real-world usefulness of this method. Further work...

@@

- We chose our initial paper because of its use of Monte Carlo. After working with it for a little it was brought to our attention that Monte Carlo was used in conjunction with a backward/forward sweep method in order to calculate the pdf. After some confusion it was decided to switch to another paper dealing with the same data/motivation but without said methods (including Monte Carlo).
- Luckily, the week after we switched papers we begun learning about bootstrapping, a way to sample from our data while taking into consideration our time change.

INSERT GRAPHS FROM IID BOOTSTRAPPING AND BLOCK HERE
ALSO INSERT FIG 1 FROM PAPER

- The paper focused most of their sampling on night-day clustering, showing the difference between night and day through current. Night yielded thousands of 0 current values, leading to skewed data when sampling. Instead we took too approaches to bootstrap the current vs. hour data.
- One using non-overlapping blocks sampling from the 8 hours surrounding the peak irradiance. The other being IID, yielding dependence in our data.

>>>>

These estimates provide consumers with an answer to 
a very pressing question. As discussed in the introduction, one of the biggest 
problems about purchasing a solar panel is whether or not 
it will end up paying for itself. One of the three stipulations in 
order to calculate your average yearly return is a solar 
panels output. After using bootstrapping we were able to 
calculate a solar panel in Los Angeles' production 
output being `r round(power_out_est_year/1000)`. Now, all 
that is needed is the peak hours and total average cost/kWh. 
The former can be calculated by setting a lower floor on 
solar irradiance. Stated on Solar Reviews, 
"1 peak sun hour" is equal to, "1000 W/m² of sunlight 
per hour", meaning our length used initially for an hour window 
would be considered peak hours. Taking this total of `r length(HOUR_WINDOW)` 
peak hours and our average cost per kilowatt-hour of /$0.03 from before 
we would find that on average a consumer in Los Angeles can 
anticipate earning /$`r round(power_out_est_year/1000,2)*.03*length(HOUR_WINDOW)` yearly on one solar panel grid. 
Knowing this, any resident located in or around the Los Angeles area should
feel confident in their decision of purchasing a solar panel unit.

The power estimate generated in this study has practical applications 
in real-world electrical engineering problems. An allocation must be 
made that balances the expected contribution of renewable energy 
sources with the expected residual demand on the electrical grid. 
An intelligent estimate of the contribution from PV modules must account 
for geographical deviations in solar irradiance. While the estimate here 
was made for Los Angeles, this framework can be applied to any location 
for which irradiance data is tracked. This framework could also be applied to 
intervals of time where power estimates could be made for each hour of the 
day or for each day of the year; greater stratified specificity would 
improve the real-world usefulness of this method.

In regard to consumer usage, an automated website could be created 
related to the information received in this paper. A simple 
user input of location could pull all the values necessary to caluclate
a predicied solar irradiance and transform that 
information, as we did above, into an estimate of total yearly 
solar panel energy cost return. This may not even just be important 
information to jsut consumers, considering the push of renewable energy 
research in the last few years by the US governement, this could be used
to find the best areas in the US to began creating large-scale solar plants. 
Finding the best city throughout the US in which NREL holds data on would turn 
our problem into an optimization one.

@@
